How cryptic is cryptic diversity? Machine learning approaches to fine scale variation in the morphology of \textit{Emys marmorata}.

### 2013-05-10 documents/turtle_presentation.Rnw
new analysis. need to fix and run randomization.

#source('../src/plotting_functions.r')
#load('../src/turtle_analysis.r')
@

@@

\begin{frame}
  \frametitle{\textit{Emys marmorata}}
  % picture of a turtle
  % this is the study system
  % a little natural history
  % a little biogeography
\end{frame}

@@

\begin{frame}
  \frametitle{Phylogenetic hypotheses}
  % images of the different phylobiogeographic hypotheses from the different spinks papers
\end{frame}

\section{Methods}
\begin{frame}
  \frametitle{Methods: morphometrics}
  % two columns, text on one side and idealized landmarks on the other
  % ken probably has an image for the landmarks
  % these landmarks have been used before in other studies
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
        \item plastral (``belly'') shape
        \item landmarks averaged across bilat axis
        \item total 13 landmarks, 7 on bilat axis, 6 off
        %\item \Sexpr{nrow(turtle.adult)} adult individuals
        \item geographic information known/inferred
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      idealized plastral landmarks
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Methods: unsupervised learning}
\end{frame}

\begin{frame}
  \frametitle{Methods: supervised learning}
\end{frame}

\section{Results}
\begin{frame}
  \frametitle{Results: mophometrics}
\end{frame}

\begin{frame}
  \frametitle{Results: gap clustering}
\end{frame}

\begin{frame}
  \frametitle{Results: d-EAC}
\end{frame}

% model selection is unnecessary because of time constraints
\begin{frame}
  \frametitle{Results: multinomial logistic regression}
\end{frame}

\begin{frame}
  \frametitle{Results: neural networks}
\end{frame}

\begin{frame}
  \frametitle{Results: random forests}
\end{frame}

>>>>

source('../src/plotting_functions.r')
#load('../src/turtle_analysis.r')
@

@@

\begin{frame}
  \frametitle{\textit{Emys marmorata}}
  % picture of a turtle
  % this is the study system
  % a little natural history
  % a little biogeography
  \begin{figure}[h]
    \centering
    \captionsetup{justification = raggedleft, slc = off}
    \includegraphics[width = 0.8\textwidth, keepaspectratio = true]{figure/turtle}
    \caption*{wikimedia}
    \label{fig:turtle}
  \end{figure}
\end{frame}

@@

\begin{frame}
  \frametitle{Phylogenetic hypotheses}

  Number of subspecies and where they occur.
  % images of the different phylobiogeographic hypotheses from the different spinks papers
\end{frame}

\section{Methods}
\begin{frame}
  \frametitle{Methods: morphometrics}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
        %\item \Sexpr{nrow(turtle.adult)} adult individuals
        \item plastral (``belly'') shape
        \item landmarks averaged across bilat axis
        \item total 13 landmarks, 7 on bilat axis, 6 off
        \item geographic information known/inferred
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \centering
      \includegraphics[width = \textwidth, keepaspectratio = true]{figure/plastra}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Methods: unsupervised learning}

  Fancy way of saying clustering or density estimation.

  Partitioning around mediods (PAM) compared with ``gap'' statistic.

  (dissimilarity based) Evidence accumulation clustering
\end{frame}

\begin{frame}
  \frametitle{Methods: supervised learning}

  Fancy way of saying classification and regression.

  Here, features (principal components) predict class (subspecific assignment).

  Multnomial logistic regression

  Random forests
\end{frame}

\begin{frame}
  \frametitle{Methods: model training and selection}
  Unknown appropriate number of features to ``best'' predict class. Want to minimize false positive, while maximizing true positive.

  Split data set, 75-25, training and testing.

  Tuning parameters via grid-search. Uncertainty via 10-fold cross-validation.

  Multinomial logistic model selected via min AICc. Random forest model via max AUC ROC.

\end{frame}
%\begin{frame}
%  \frametitle{Methods: ROC}
%\end{frame}

\section{Results}
\begin{frame}
  \frametitle{Results: mophometrics}
<<gm, eval = FALSE>>=
morph <- ggpairs(turtle.adult, columns = c(1:3),
                 upper = 'blank')
fits <- procGPA(turtle.land.adult)
land <- mshape.plot(fits, all.points = TRUE)
morph <- putPlot(morph, land, 1, 3)
morph
@
\end{frame}

\begin{frame}
  \frametitle{Results: gap clustering}
<<gap, eval = FALSE>>=
gap <- gap.plot(tadult.gap)
gap
@
\end{frame}

\begin{frame}
  \frametitle{Results: d-EAC}

\end{frame}

% model selection is unnecessary because of time constraints
\begin{frame}
  \frametitle{Results: multinomial logistic regression}

\end{frame}

\begin{frame}
  \frametitle{Results: random forests}
  % plot the ROC curves
  % four facets, multiple lines
\end{frame}
